Joint analysis of read count data

### 2020-09-04 combined_analysis/combine_all_data.Rmd
Fix Dx

```{r plots.interaction.DxSex, fig.width=10, fig.height=5}
# Disease
tab = topTable(fit_marginal, "SczSex", number=Inf) %>% getGeneSymbol
fig1 = plotVolcano( tab, tab$Symbol[1:20] ) + ggtitle("SCZ")

tab = topTable(fit_marginal, "BPSex", number=Inf)  %>% getGeneSymbol
fig2 = plotVolcano( tab, tab$Symbol[1:20] ) + ggtitle("BP")

>>>>

```{r plots.interaction.DxSex, fig.width=10, fig.height=5}
# Disease
tab = topTable(fit_interaction_DxSex, "SczSex", number=Inf) %>% getGeneSymbol
fig1 = plotVolcano( tab, tab$Symbol[1:20] ) + ggtitle("SCZ")

tab = topTable(fit_interaction_DxSex, "BPSex", number=Inf)  %>% getGeneSymbol
fig2 = plotVolcano( tab, tab$Symbol[1:20] ) + ggtitle("BP")
